### 2025-03-06 tutorials/getstarted.qmd
Update tutorials/getstarted.qmd
Co-authored-by: Mateusz Baran <mateuszbaran89@gmail.com>
A get-started tutorial (#24)
* Start tutorial.
* Improve technical details print.
* Continue the tutorial.

---------

Co-authored-by: Mateusz Baran <mateuszbaran89@gmail.com>

The left-invariant metric is in general not right-invariant, except for compact Lie groups and their direct products with Translations.

@@

and look at the manifold dimension, it is the sum of the single ones

@@

and its coordinates as

>>>>

The left-invariant metric is in general not right-invariant, except for compact Lie groups and their direct products with translations, see for example [LatifiToomanian:2013](@cite) for an even more general proof.

@@

and look at the manifold dimension, it is the sum of dimensions of its components

@@

The coordinates of `Y` are
